---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Juan Ratto"
date: "2/3/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The sinking of the Titanic: predicting survival (ShinyApp)

We use the titanic dataset for write a shiny app for predict the survival probability in the sinking of the titanic.

- The link of the app: <https://juandratto.shinyapps.io/ShinyApp_ReprodPitch/>.
- The link of github repo: <https://github.com/juandratto/ShinyAppAndReprodPitch>.

For detailed information about the titanic dataset: <https://www.kaggle.com/c/titanic>.

## Titanic dataset analysis

Selecting only the Pclass, Age, Sex and Embarking variables.

```{r titanic, echo = TRUE,  message=FALSE}
library(caret)
library(rpart)

set.seed(1234)
df_titanic_training <- read.csv("titanic_train.csv")
df_titanic_training <- df_titanic_training[,-c(1)]

summary(df_titanic_training)

```

## Using Random forest model

```{r modrf, echo=FALSE, message=FALSE}
library(rpart)
library(rpart.plot)
mod_rf <- rpart(Survived ~ ., data = df_titanic_training, method = "class")
rpart.plot(mod_rf)

```

## Predicting Survival

```{r pred01, echo=TRUE, message=FALSE}

        pclassInput <- 1
        SexInput <- "male"
        AgeInput <- 33
        EmbarkInput <- "C"
        
        newdata <- data.frame(Pclass = pclassInput, Sex = SexInput, Age = AgeInput, Embarked = EmbarkInput)
        
        pred <- predict(mod_rf, newdata = newdata)
        paste0(format(as.numeric(pred[1,2])*100, digits = 2), "%")
```

